Gsmodutils: A python based framework for test-driven genome scale metabolic model development

### 2018-09-27 article/article.tex
missing figure

\begin{acknowledgement}
We would like to thank the Oxford Brookes Cell Systems Modelling group for helpful discussions regarding this work and for scientific advice.
This work was supported by the UK Biotechnology and Biological Sciences Research Council (BBSRC) grants BB/L013940/1,  BB/K00283X/1 and BB/L502030/1.
\end{acknowledgement}

>>>>

\begin{acknowledgement}
We would like to thank the Oxford Brookes Cell Systems Modelling group for helpful discussions regarding this work and for scientific advice.
This work was supported by the UK Biotechnology and Biological Sciences Research Council (BBSRC) and Engineering and Physical Sciences Research Council (EPSRC) grants BB/L013940/1,  BB/K00283X/1 and BB/L502030/1.
\end{acknowledgement}
